---
title: "Binomir Walkthrough"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Binomir Walkthrough}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
  
)
library(binomir)
```

Welcome to binomir, a package designed for ease of access to the binomial distribution. All functions will check that the inputs are conceptually valid.

### The Binomial Distribution
A binomial distribution is, at it's core, a sum of independent bernoulli trials. So a binomial distribution has two parameters: the number of trials and the probability of success on each distribution. In most functions in this package they call the parameters trials and prob.

The probability density function for a binomial denstity is the following:

$$P(X = k) = {n\choose k} p^k p^{n - k} $$

where ${n\choose {k}} = \frac{n!}{k!(n - k)!}$, n is the number of trials, p is prob, and k is the number of desired successes.

This can be computed using the function `bin_probability()`, which uses `bin_choose()`.

##### Example:
```{r}
bin_choose(n = 5, k = 1)
bin_probability(prob = .5, trials = 5,  success = 1)
```

bin_probability can also be used with multiple successes for multiple probability results.

##### Example:
```{r}
bin_probability(trials = 5, prob = .5, success = 0:5)
```

There are also functions to tabulate the entire binomial density function along with its cumulative density function. Each of these functions have the parameters trials and prob. These are `bin_distribution()` and `bin_cumulative()`. The cdf is also contained in the output of `bin_cumulative()`.

##### Example:
```{r}
bin_distribution()
bin_cumulative()
```

Now, these functions output objects of classes `c("bindis", "data.frame")` and `c("bincum", "data.frame")`. 

This package contains methods for plotting objects of class `"bindis"` and `"bincum"`. This method requires the package "ggplot2".

##### Example:
```{r}
x <- bin_distribution(trials = 50, prob = .3)
class(x)
plot(x)

y <- bin_cumulative(trials = 50, prob = .3)
class(y)
plot(y)
```


## Summary statistics:
The package also has functions to compute the following summary statistics: mean, variance, mode, skewness, and kurtosis. Each of these functions have the parameters trials and prob.

##### Example:
```{r}
bin_mean()
bin_variance()
bin_mode()
bin_skewness()
bin_kurtosis()
```

## `"binvar"` object class
The function `bin_variable()` has two inputs trials and prob, and outputs a list of class `"binvar"`. This object contains the two parameters of the binomial distribution. This package comes with a method for summary for objects of this class. The `summary()` of an object of class `"binvar"` is a list containing the previous summary statistics but with the number of trials and prob from the `"binvar"` object. There are also methods for the printing of the `"binvar"` object and its summary.

##### Example:
```{r}
x <- bin_variable(trials = 5, prob = .5)
class(x)
x

summary(x)
```


